Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-06-19 inst/doc/nonparametric-bayes.Rmd

```{r plot-options, echo=FALSE, cache=FALSE, include=FALSE}
options(xtable.print.comment=FALSE)
options(xtable.type = 'latex', table.placement="H")
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(dev = 'Cairo_pdf', fig.width=5.5, fig.height=4,
 cache.path = 'cache/nonparametric-bayes/', cache=TRUE, external=TRUE)
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA,
               tidy=FALSE, echo=FALSE)
```

>>>>

```{r plot-options, echo=FALSE, cache=FALSE, include=FALSE}
options(xtable.print.comment=FALSE)
options(xtable.type = 'latex', table.placement="H")
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(dev = c('pdf', 'png'), fig.width=5.5, fig.height=4,
 cache.path = 'cache/nonparametric-bayes/', cache=TRUE, external=TRUE)
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA,
               tidy=FALSE, echo=FALSE)
```
